Software Citation Principles

### 2016-05-09 sc-principles/software-citation-principles.tex
fix typo

While we often need to cite a specific version of software, we may also need a way to cite the
software in general, or the latest version, and to link multiple releases together, perhaps for
the purpose of understand citations to the software.  The principles in \S\ref{sec:principles} are
intended to be applicable at all levels, and to all types of identifiers, such as DOIs, RRIDs, etc.,
though we again recommend when possible the use of DOIs that identify specific versions of
source code.  We note that RRIDs were developed by the FORCE11 Resource Identification Initiative
and have been discussed for use to identify software packages (not specific versions),
thought the FORCE11 Resource Identification Technical Specifications Working
Group~\cite{f11rrridtswg} says ``Information resources like software are better suited to
the Software Citation WG.''
There is currently a lack of consensus on the use of RRIDs for software.

>>>>

While we often need to cite a specific version of software, we may also need a way to cite the
software in general, or the latest version, and to link multiple releases together, perhaps for
the purpose of understanding citations to the software.  The principles in \S\ref{sec:principles} are
intended to be applicable at all levels, and to all types of identifiers, such as DOIs, RRIDs, etc.,
though we again recommend when possible the use of DOIs that identify specific versions of
source code.  We note that RRIDs were developed by the FORCE11 Resource Identification Initiative
and have been discussed for use to identify software packages (not specific versions),
thought the FORCE11 Resource Identification Technical Specifications Working
Group~\cite{f11rrridtswg} says ``Information resources like software are better suited to
the Software Citation WG.''
There is currently a lack of consensus on the use of RRIDs for software.
